---
title: "How to publish slides with Github"
author: "Hendrik Jürges"
date: "19 11 2021"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Create doc

1. Create directory on harddisk
2. Create R project
```{r eval=FALSE}
usethis::create_project("filepath/for/your/presentation/repo-name")
```
3. Create presentation or other html-file

## Connect project with Github

4. Initialize version control with git. Say yes to both prompts
```{r eval=FALSE}
usethis::use_git()
```
5. Connect your local project with a GitHub repo (possibly with option `private = TRUE`)
```{r eval=FALSE}
usethis::use_github()
```

## Make and commit changes

The next steps happen in the terminal!

```{r eval=FALSE}
# Step 1: Stage all modified files
git add .
# Step 2: Describe the changes you made to your files
git commit -m "<A brief but descriptive commit message>"
# Step 3: Push the changes to your GitHub repository
git push
```

## Deploy slides

```{r eval=FALSE}
usethis::use_github_pages(branch = "master")
```

- Only need to follow this step once to deploy your slides to the web
- As long as you remember to push to your repo any changes that you make to your slides (Rmd and HTML), GitHub Pages will know how to render them
